\chapter{Project Management \& Self Review}

\section{Gantt Chart \& Amendments}
The full pre-amendment Gantt chart can be found \href{https://www.notion.so/zuddas/9c097f57d9d844da8fc7f8733b38289f?v=61d021af0d9d40ebab7b2a6fbe6b3bd8}{here}. 
The full post-amendment Gantt chart can be found \href{https://www.notion.so/zuddas/ee42fe3d801947d08c59b69aa2e4f0cd?v=13936a7a4a4a4cff9e9fc01ff24508cb}{here}. 

Figure \ref{fig:S2Gantt} shows the amended Gantt chart for Semester 2. Amendments were made to extend the time allocated to the development, validation and appraisal of the \ac{ABM}. This was done to allow more than enough time to iron out related development problems related to making the model work in conjunction with surrounding software. There will be iterative development processes performed during the model development, firstly focusing on developing core aspects of the \ac{ABM} such as the agents themselves and their interactions with the environment and event generator. Gradually, development will expand to include the more complex features, such as the social network, as well as make the \ac{ABM} work with other software such as MATLAB to process inputs and outputs. 



\section{Self-Review}


Overall the project has seen good progress since the start of the semester. There has been excellent supervision and support on behalf of my supervisor. 

The research aspect of the project proved relatively challenging as there were many new concepts to learn in a field in which I had no expertise (public health). Nonetheless, I feel I have gained a relatively good understanding of the topics related to public health given the \ac{ABM} is the core focus of the project. There was less difficulty in apprehending concepts related to \ac{ABM} as it is a topic in which I was formally taught in the semester and had done some previous work on. 

There have been technical difficulties in using software and installing the various dependencies related to \ac{RHPC} both on my laptop and in the Linux remote server \cite{repasthpc}. This led to programming being slower than intended, and is a sign that work will have to be done over Christmas in order to compensate. The issues presented a challenge in understanding various computing concepts that were previously unknown to me, but they've extended my understanding of how computers work more generally. They are now mostly resolved and programming work can progress but there are still some issues that when overcome will lead to a more streamlined development process. 